Exploring Real Data: A look at AirBnB

### 2017-06-07 ArticleDraft.Rmd
Changed 1st violin plot color

```{r, echo = showcode,fig.height = 2,fig.width = 5}
#First we filter our data so that only includes the neighbourhood we care about: 
seattle1<-seattle %>% filter(neighbourhood_cleansed == 'Alki')

@@

#Create a boxplot + violin plot to see what prices happen most: 
ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'cyan')+
  geom_boxplot(width = .3, fill = 'Lightblue')+coord_flip() + xlab('') + ylab('Price')+
  ggtitle('Distribution of Prices in the Alki Neighborhood')
```

>>>>

```{r, echo = showcode,fig.height = 2.5,fig.width = 5}
#First we filter our data so that only includes the neighbourhood we care about: 
seattle1<-seattle %>% filter(neighbourhood_cleansed == 'Alki')

@@

#Create a boxplot + violin plot to see what prices happen most: 
ggplot(seattle1, aes(x = 'Alki', y = price)) + geom_violin(fill = 'mediumorchid3')+
  geom_boxplot(width = .3, fill = 'mediumorchid1')+coord_flip() + xlab('') + ylab('Price')+
  ggtitle('Distribution of Prices in the Alki Neighborhood')
```
